%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage[default,osfigures,scale=0.95]{opensans} %% Alternatively
%% use the option 'defaultsans' instead of 'default' to replace the
%% sans serif font only.
\usepackage[T1]{fontenc}

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=9.0in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{} 

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\large\bf Peer Allan \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
27 Jupiter Bay \\ Winnipeg, MB Canada R3T 0W5 \\ 1.204.233.0052 % Your address and phone number
\end{center} 
\vfill

\signature{Peer Allan} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Mr. Vogel,} 

You have asked for a developer that has great ideas and can keep up with a rapidly changing marketplace. My years of web application development experience is an excellent match for these needs. Information security is an amazing topic that may not look like much on the surface, but it can have amazing depth and complexity. Working in such an environment is a very exciting prospect.

My present experience with Information Security is limited. As part of this experience, I have had to ensure the security of web based applications, servers and databases. PCI compliance is a topic I am deeply investing into at present as we move to upgrade our systems to be compliant. This experience level will create a highly motivated employee for your company as I learn everything that I can about your business in order to serve it to the best of my abilities.

The 403 Labs job posting details many skills that are necessary for the position: Ruby/RubyOnRails, Web technologies, REST, TDD, RDBMS and HTTP scalability. In each of these areas my experience will serve your company well. I have been working on the web for 12 years (HTML, CSS, Javascript), 7 years with Ruby/RubyOnRails, 4 years with REST and 10 years RDBMS with MySQL. All the while I have been honing these skills on the Linux or MacOS X command line.

As for me, I am a father of 3 girls. I used to play hockey, now I just watch it. I tend to be competitive and I get my fix by curling (I am Canadian). My  personal goal this next year is to start doing triathlons and (maybe one day) complete an Ironman. Hopefully, it will be obvious that I love to program and probably spend to much time doing it in the evening. Work-life balance is important to me as I want to spend time with my kids before they don't want to spend time with me. I am looking for an opportunity to work for a company where this is possible.

Please check out my Github profile for examples of some projects have contributed to in the past. Thank you for your time and considerations. I look forward to speaking with you and discussing my qualifications in more detail.

\closing{Sincerely yours,}



re: http://www.403labs.com/about/join/developer
github: https://github.com/pallan
%\encl{Resume} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}